PLUNGER: Reproducing FLUSH+RELOAD: A High-Resolution, Low-Latency Side Channel Attack On GnuPG

### 2014-12-17 paper/paper.tex
time $T$ -> interval $T$

The \flushreload{} attack takes advantage of page deduplication on modern
processors. The basic attack works as follows: the attacker loads into memory
some block of data that it believes the victim to also be accessing. The system
then deduplicates these two identical pages. The attacker can then use the
instruction \texttt{clflush} to flush memory lines in that block from the CPU caches. The
attacker then waits for some time $T$ and attempts to access a memory line
in this page, and measures the time (in cycles) it takes for the line to be
loaded. If the memory line was accessed by the victim during $T$, the time taken
will be shorter because it will be cached, and if it was not accessed, the time taken will be longer.
Consequently, the attacker can determine if the line was accessed during $T$.

>>>>

The \flushreload{} attack takes advantage of page deduplication on modern
processors. The basic attack works as follows: the attacker loads into memory
some block of data that it believes the victim to also be accessing. The system
then deduplicates these two identical pages. The attacker can then use the
instruction \texttt{clflush} to flush memory lines in that block from the CPU caches. The
attacker then waits for some interval $T$ and attempts to access a memory line
in this page, and measures the time (in cycles) it takes for the line to be
loaded. If the memory line was accessed by the victim during $T$, the time taken
will be shorter because it will be cached, and if it was not accessed, the time taken will be longer.
Consequently, the attacker can determine if the line was accessed during $T$.
